First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-27 ms.tex
spacing
BMG comment

In addition to a point source foreground model, we also introduce a diffuse emission model 
within the primary field of view of the MWA. Though the EoR0 field was chosen to be 
relatively devoid of Galactic emission, we find this diffuse structure still highly contaminating 
due to the very high sensitivity of the MWA at large scales. For computational purposes we 
have divided the Galactic emission into two regimes -- the faint clouds in our main lobe, and 
the bright plane and other structures in the sidelobes. While the latter has been studied by 
many people and a Global Sky Model (GSM) is readily available 
\citep{deOliveira-Costa:2008}, the computational obstacle of simulating the instrument 
response to a full sky diffuse model is yet prohibitive, though under active pursuit 
\citep{Thyagarajan:2015}. We instead focus here on diffuse structure within the primary field 
and leave the full-sky model to future iterations of analysis.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.
The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.

>>>>

In addition to a point source foreground model, we also introduce a diffuse emission model 
within the primary field of view of the MWA. Though the EoR0 field was chosen to be 
relatively devoid of Galactic emission, we find this diffuse structure still highly contaminating 
due to the very high sensitivity of the MWA at large scales. For computational purposes we 
have divided the diffuse emission into two regimes -- the faint clouds in our main lobe, and 
the bright plane and other structures in the sidelobes. While the latter has been studied by 
many people and a Global Sky Model (GSM) is readily available 
\citep{deOliveira-Costa:2008}, the computational obstacle of simulating the instrument 
response to a full sky diffuse model is yet prohibitive, though under active pursuit 
\citep{Thyagarajan:2015}. We instead focus here on diffuse structure within the primary field 
and leave the full-sky model to future iterations of analysis.

@@

The RTS uses a fundamentally different calibration and foreground subtraction approach than 
FHD, as well as a different input point source model. 
The primary differences lie in the 
bandpass calibration, the use of ionospheric corrections, and the lack of a diffuse model. The 
calibration model uses a model with 1000 sources, for which ionospheric corrections are 
estimated and applied, before peeling of those sources from the dataset. The bandpass 
calibration is fundamentally different to FHD.
The bandpass for each antenna is fitted to a 2nd order polynomial within each 1.28~MHz coarse 
band individually. The delay of the 150~m cable reflection discussed earlier is comparable
to the scale of the polynomial fit, so we expect it to naturally be fit out of the gain
solutions. Indeed the RTS has not yet seen evidence of the reflection in the processed
data \citep{Jacobs:2016}.

The CHIPS power 
spectrum estimator applies a full maximum-likelihood estimator to the data. In its full form, the 
data are weighted by the thermal noise, and a model for the residual point source signal, 
within a full frequency-dependent description of the instrument. For this comparison, the 
foreground weighting is not used, in order for a direct comparison with the weighting scheme 
used by \eppsilon.
